Re-envisioning a future in scholarly communication

### 2017-05-28 manuscript.Rmd
Update draft

---
title: "Re-envisioning a future in scholarly communication"
author: "Chris H.J. Hartgerink"
date: '`r Sys.Date()`'
output:
  html_document:
    includes:
      in_header: hypothesis.html
  word_document: default
fig_caption: yes
bibliography: library.bib
---

>>>>

---
title: "Re-envisioning a future in scholarly communication"
author: "Chris H.J. Hartgerink"
date: '`r Sys.Date()`'
output:
  pdf_document: default
  html_document:
    includes:
      in_header: hypothesis.html
  word_document: default
fig_caption: yes
bibliography: library.bib
---
